\section*{Executive Summary (Fabio)}
\begin{spacing}{1.5}
The Marine Operated Stereoscopic Imaging System (M.O.S.I.S) is an underwater microscope that can capture stereoscopic images and environmental conditions simultaneously. The goal of this project was to create a new user interface for the M.O.S.I.S microscope that reflects the current state of the system. We were successfully able to create a new user interface that integrates, the on board lighting systems, cameras and buttons that can capture various kinds of images and video. More specifically, the microscope can capture single, burst, time lapse and telescopic images and video using either white, red or ultraviolet lighting. There was a delay of 12 days from the projected integration date due to unforeseen problems with the system responsiveness and the amount of worked involved in integrating the sensors and buttons that was severely under estimated. The sensors and the on board buttons were able to be successfully integrated by the demonstration date using the buffer time in the schedule, however, the system responsiveness issues would require a complete redesign of the user interface which could not be achieved given the strict time constraints of the project. The actual budget cost at the end was \$33,771.60. The difference between the actual budget and the estimated was the equipment cost, since it took into account the cost of the laptops and M.O.S.I.S microscope. The potential customer base for the M.O.S.I.S microscope and the newly created user interface would be universities, specifically marine biology and environmental scientist researchers looking for a device to expedite their research.
\end{spacing}