\section{Requirements (Fabio \& Eduardo)}
\subsection{Domain Requirements}
\begin{itemize}
	\item The system-to-be must present the left and right camera feeds to the user.
	\item The system-to-be must present temperature, Ph, dissolved oxygen, pressure and local IP address to the user.
	\item The system-to-be must have the means to switch between different study profiles
        \item The system-to-be must control the lighting on the microscope camera according to the study profile.
        \item The system-to-be must control the shot type on the microscope camera according to the study profile.
	\item The system-to-be must have a database that stores:
	      \begin{itemize}
		      \item Left Camera Media
		      \item Right Camera Media
		      \item Shot type
		      \item ISO 8601 Time Stamp
		      \item Temperature
		      \item Ph
		      \item Pressure
		      \item Dissolved Oxygen
	      \end{itemize}
	\item The system-to-be must store the captured data into a browsable format.
	\item The system-to-be must use the on board buttons.
\end{itemize}
\subsection{Interface Requirements}
\begin{itemize}
	\item The system-to-be must present the feed from left and right cameras, each at 15FPS and a downscaled 400x400 resolution.
	\item The system-to-be must present: temperature, Ph, pressure, dissolved oxygen and IP address.
	\item The system-to-be must update temperature, Ph, pressure, dissolved oxygen and local IP address every two seconds.
        \item The system-to-be lighting enumeration contains:
          \begin{itemize}
          \item None
          \item Infrared
          \item Ultraviolet
          \item Visible Spectrum
          \end{itemize}
        \item The system-to-be shot type enumeration contains:
          \begin{itemize}
          \item Single
          \item Burst
          \item Telescopic
          \item Time Lapse
          \item Video
          \end{itemize}
	\item The system-to-be must initiate a capture with a single button.
	\item The system-to-be must shutdown the operating system safely with a single button.
	\item The system-to-be must stop capture with a single button.
	\item The system-to-be must be able to navigate through the study profiles using only two buttons.
	\item The system-to-be must show the currently loaded study profiles using a single button.
	\item The system-to-be must store all files related to a single study entry in a single location.
        \item The system-to-be must store a JSON file with all data and metadata from the study entry along in the same folder as the study entry.
	\item The system-to-be must control the focus of the cameras one stepper motor step at a time using two of the board buttons.
\end{itemize}